An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2019-03-19 paper/main.tex
added methods fig to paper

@@

Prior work has shown participants share similar neural responses to richly structured stimuli when compared to stimuli with less structure.  To assess whether the moment-by-moment higher order correlations were reliably preserved across participants, we used inter-subject functional connectivity (ISFC) to isolate the time-varying correlational structure (functional connectivity patterns that were specifically driven by the story participants listened to.  Following the analyses conducted by (HTFA)~\cite{MannEtal18},, We first applied HTFA to the fMRI datasets to obtain a time series of 700 node activities for every participant.  We then computed the dynamic weighted ISFC using a gaussian kernel with a width of 5. We then approximated these dynamic correlation using PCA and computed the dynamic weighted ISFC on the approximations.  We repeated this process up to 10th order approximated correlations.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods_fig}
  \caption{\textbf{Examples of time-varying weights.  Each panel
      displays per-timepoint weights at $t = 50$, evaluated for 100
      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
    are timepoint-invariant; observations at all timepoints are
    weighted equally, and do not change as a function of $t$.  This is
    a special case of weight function that reduces dynamic
    correlations to static correlations. }
  \label{fig:methods_fig}
\end{figure}

@@

Prior work has shown participants share similar neural responses to richly structured stimuli when compared to stimuli with less structure.  To assess whether the moment-by-moment higher order correlations were reliably preserved across participants, we used inter-subject functional connectivity (ISFC) to isolate the time-varying correlational structure (functional connectivity patterns that were specifically driven by the story participants listened to.  Following the analyses conducted by (HTFA)~\cite{MannEtal18}, We first applied HTFA to the fMRI datasets to obtain a time series of 700 node activities for every participant.  We then computed the dynamic weighted ISFC using a gaussian kernel with a width of 5. We then approximated these dynamic correlation using PCA and computed the dynamic weighted ISFC on the approximations.  We repeated this process up to 10th order approximated correlations.
